\section{General Provisions}

The competitions will be conducted in accordance with the Competition Regulations (WB), the legal system (RO), the competition license order (WLO) and the Anti-Doping Rules (ADO) of the German Swimming Association (DSV). Presenter and organizer is the Schwimmteam Erzgebirge. All registered athletes, trainers, and accompanying persons give their consent to photography, audio and video recording and their release, publication and reproduction to be used for promotional purposes, inclusion on websites, social media and any other purposes related to the competition’s organization, reporting and promotion.

For handicapped persons or athletes with special needs with appropriate classification verification the competition regulations of the German Disabled Sports Association (DBS) apply additionally. Participation is open to members of club/teams, which belong to the DSV Swimming Association and possess the association rights, as well as all foreign organizations and associations, as long as their national associations are FINA members, and who have the right to start. Athletes born 2015 and younger are only allowed to start 6 times a day including relays.

The “one start rule” will apply.  The organizer of the swim competition and the operator of the aquatic facility are not responsible for lost and damaged items. By entering the aquatic facility, you agree to all its terms and conditions. 
The German Swimming Federation (DSV) and the Swimming Federation of Saxony (SSV) were notified about the International Erzgebirgsschwimmcup.
