\section{Registration}

All participating clubs must register by e-mail in the DSV/LENEX standard. Please attach a control printout of the registration. Registrations without reporting times or with incorrect information will be rejected. According to the DSV competition regulations the registration must include the statement about the athlete's health.

The organizer reserves the right to reject registrations, to change the start times and/or to reschedule individual events if necessary due to registration numbers. For the 200 m distances, a maximum of 3 heats per event will be admitted – for 200 m individual Medley a maximum of 5 heats per event will be admitted. The athletes with the fastest reporting times will start. The organizer reserves four starts per distance for its own athletes. Best performances count from \athleteBestDateEN. For the 200 m distances the organizer compares the reporting time with the DSV ranking. For the 100 m distances, the standard times apply.
 
\textbf{Registration deadline is Tuesday, \registrationDeadlineEN.} Post-deadline registration and changing registrations are not possible. In order to ensure a fast course of events, \textbf{please notify us about sick athletes by Thursday, \deregistrationDeadlineEN} via e-mail. All participating clubs will receive a confirmation of their registrations. You will also be informed in case of rejected registrations and if the start times have changed until Sunday, \entryConfirmationDateEN.

The heat organization for each age group takes place according to reporting times. The heat organization of the 200 m distances will take place based on reporting times only. For the 100 m distance we have limits.
  
All participating teams of 5 athletes or more, or 20 or more starts, are obliged to provide a swimming judge or a referee to own costs. Teams of 21 athletes or more, or 100 or more starts are required to provide 2 swimming judges. The judge/referee registration has to be made until the deadline including the qualification level, the name as well as preferred assignment. All referees will receive free food and an event t-shirt free of charge.

The results report and the protocol as a hardcopy will only be prepared if requested during registration. Both results and protocols will be available online on the website \textbf{erzgebirgsschwimmcup.de} and in the \textbf{SwimResults app}.

The start fee per single start (50/100 m) is \entryEarly\ euros for teams with at least 100 starts and registrations received by \earlyRegistrationDateEN; all other 50/100 m entries cost \entrySingle\ euros. Each 200 m entry and each relay costs \entryRelay\ euros. If the registration does not meet the valid DSV standard there will be additional charges of \entryFormatPunishment\ euros per registration. For each not provided referee \entryRefreePunishment\ euros are charged.

{\textbf{
\begin{tabular}{rl}
    Registration Address:   & Alexander Steiner\\
			        & Hammergasse 24\\
			        & 09526 Olbernhau\\
			        & Deutschland - Germany\\
	Phone:          & +49 37 36 07 51 77\\
    Mobile          & +49 16 26 80 21 60\\
    E-Mail:         & alex@schwimmteamerzgebirge.de\\
    Web:            & schwimmteamerzgebirge.de
\end{tabular}
}}

Please transfer the registration fee to the following account of the
ST Erzgebirge, Volksbank Chemnitz.\\
\textbf{IBAN \bankIBAN\ / BIC \bankBIC}
