\section{Honors and Awards}

The top three of each rating will receive \textbf{medals}. \textbf{Certificates} will be awarded through sixth place and made available for all places at erzgebirgsschwimmcup.de and in the SwimResults app. The best women’s and men’s performance is honored with \textbf{high-quality swimwear} and the \textbf{trophy} of the mayor of the Bergstadt of Marienberg. At 900 DSV points an additional \textbf{cash prize} of \textbf{\awardNinehundretDSV\ euros} is paid, provided there are at least 2{,}000 guest-club entries.
New hall records are rewarded with \textbf{cash prizes}, \textbf{\awardPoolRecord\ euros}; at 900+ DSV points \textbf{\awardPoolRecordNinehundretDSV\ euros}. The best performance in each category will be awarded a \textbf{trophy} and a \textbf{swimsuit} or a \textbf{trunk}. In the event of a tie, the athlete’s second-best performance is used.

In all finals at least the following \textbf{cash prizes} will be awarded:	
1st \textbf{\awardAFinalFirst\ euros}, 2nd \textbf{\awardAFinalSecond\ euros}, 3rd \textbf{\awardAFinalThird\ euros}, 4th \textbf{\awardAFinalFourth\ euros}.

At the junior finals (2009 female and 2008 male and younger), provided there are 2{,}000+ guest entries, the following \textbf{premiums}: 
1st \textbf{\awardBFinalFirst\ euros}, 2nd \textbf{\awardBFinalSecond\ euros}, 3rd \textbf{\awardBFinalThird\ euros}, 4th \textbf{\awardBFinalFourth\ euros}

The winner relays will be honored with real challenge cup of the region „Erzgebirge". In all announced scorings the following points will be assigned: 1st 12, 2nd 8, 3rd 5, 4th 3, 5th 2, 6th 1 point(s). For each scoring, the two best athletes from each club will receive points. The finals as well as the relays will score twice as much points as a normal event. The junior finals score single points. The point best team of the whole competition will receive the \textbf{Erzgebirgsschwimmcup}, the point best team of the first competition day receives the \textbf{Junior-Erzgebirgsschwimmcup}. Both honors are eternal challenge cups. For the \eventIteration th time that the IESC takes place we honor the best team with \textbf{\awardClubFirst\ euros}, the second-best team with \textbf{\awardClubSecond\ euros} and the third-best team with \textbf{\awardClubThird\ euros}. The ranking after all scoring events will count. The award ceremony is part of the competition. If you do not attend the ceremony, you forfeit all honors.
